Updates on the Exoplanet Orbit Database

### 2014-03-06 draft/ms.tex
Add ref in table, linking to sections or refer to W11.

%------------------------------------------------------------------------------
\subsection{Discovery and References}

@@

%------------------------------------------------------------------------------
\subsection{Orbital Parameters}
We report the orbital parameters that determine the shape of the
planet's orbit. Depending on the detection methods, different sets of
parameters are given by the literatures. For instance, if a planet is
detected by the radial velocity method, the semiamplitude, $K$, is
reported whereas the inclination of the orbit, $i$, is reported by the
transit method. We describe the added fields since \cite{Wright2011}
below.

@@

%------------------------------------------------------------------------------
\subsection{Transit Parameters}
We report the transit parameters, which are available only when the
planet has TRANSIT flag equal to 1. We describe added fields since
\cite{Wright2011} below.

@@

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}

@@

%------------------------------------------------------------------------------
\subsection{Stellar Properties}
This set of parameters is to provide users the physical parameters of
the exoplanet host stars.  Most of the parameters are derived from the
stellar models in the literatures and we provide the readers with the
references. We describe added fields since \cite{Wright2011} below.

@@

%------------------------------------------------------------------------------
\subsection {Stellar Magnitudes}

@@

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}
We report the coordinates of the host star as well as the stellar ID
as designated by different catalogs.  We added {\bf DIST} since
\cite{Wright2011}, which is the distance of the host star in the unit
of pc. If only parallax (PAR) is given, we convert it to DIST and vice
versa. If the literature does not report DIST or PAR, then we obtain
PAR from the Hipparcos data set by \cite{van Leeuwen2009}.

%------------------------------------------------------------------------------
\subsection{Uncertainties and Upper Limits}

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
uncertainties, and they are different when the error bars are
asymmetric. UX contains the 1$\sigma$ uncertainty, and it
equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
bars. Fields that have XUPPER, XLOWER and UX are:  all the orbital parameters except for TREND and FREEZE\_ECC flags; all the transit parameters except for TRANSIT flags; all the secondary eclipse fields except for SE flag; and all the stellar properties except for STAR, SPECREF and BINARY flag; and DIST and PAR. 
We also report the upper limits for planet mass (MSINI), eccentricity (ECC), and the velocity semi-amplitude (K) when the literatures only provide the upper limits and not the actual values. The upper limits for ECC is reported when the orbit is circular, and the upper limits for K is reported when there is no radial velocity detection. If only upper limits are given, we set the field to 0, the uncertainty to half of the upper limit, and the upper limits to the upper limits. For example, if the literature reports the upper limit for ECC, then we put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.

ZZZ modify table to reflect MASSUL, ECCUL, KUL, fields
%------------------------------------------------------------------------------
\subsection{References}

@@

\begin{deluxetable}{llll}

@@

  \colhead{Related Fields\tablenotemark{b}}

@@

NAME\dotfill & String & Name of planet & \nodata \\
OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata \\
MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata \\
STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\
ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL \\

@@

planetary orbit & FIRSTURL \\

@@

Planets Encyclopaedia & EPEURL \\

@@

Transit Database & ETDURL \\

@@

Archive database & EAURL \\

@@

planet, if available) & SIMBADURL \\

@@

\nodata \\
KOI\dotfill & Float & KOI object number & \nodata \\
KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\

@@

function) in \mjup & -UPPER, etc. \\
MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. \\
A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. \\
SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. \\
PER\dotfill & Double & Orbital period in days & -UPPER, etc. \\

@@

-UPPER, etc. \\
ECC\dotfill & Float & Orbital eccentricity & -UPPER, etc. \\
I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\
OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. \\
BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. \\

@@

& -UPPER, etc. \\
TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL \\

@@

etc. \\

@@

HJD\tablenotemark{d} & -UPPER, etc. \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. \\
B\dotfill & Float & Impact parameter of transit & -UPPER, etc. \\
AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. \\
DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\

@@

-UPPER, etc. \\

@@

-UPPER, etc. \\
DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. \\
RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. \\

@@

CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata \\
NOBS\dotfill & Integer & Number of observations used in fit & \nodata \\

@@

\nodata \\
FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata \\
TREND\dotfill  & Boolean & Linear trend in fit? & \nodata \\
NCOMP\dotfill & Integer & Number of planetary companions known & \nodata \\
MULT\dotfill & Boolean & Multiple planets in system? & \nodata \\
COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata \\

@@

been detected & -REF,-URL \\
SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. \\

@@

band & -UPPER, etc. \\

@@

\kepler\ photometry band & -UPPER, etc. \\

@@

\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\

@@

\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\

@@

\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\

@@

\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\

@@

HJD\tablenotemark{d} & -UPPER, etc. \\

@@

STAR\dotfill & String & Standard name for host star & \nodata \\
BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\
MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. \\
RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. \\
RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. \\

@@

host star in cgs unit & -UPPER, etc. \\

@@

star in k\mps & -UPPER, etc. \\
GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. \\

@@

V\dotfill & Float & $V$ magnitude & -REF,-URL \\
BMV\dotfill & Float & $B-V$ color & \nodata \\
J\dotfill & Float & $J$ magnitude & \nodata \\
H\dotfill & Float & $H$ magnitude & \nodata \\
KS\dotfill & Float & $K_S$ magnitude & \nodata \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata \\
KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata \\
SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL \\

@@

RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\
PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\
DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. \\

@@

star & \nodata \\
HD\dotfill & Long Integer & Henry Draper number of sar & \nodata \\
GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata \\
HR\dotfill & Integer & Bright Star Catalog number of star & \nodata \\
SAO\dotfill & Long Integer & SAO catalog number of star & \nodata \\

@@

column. They are...}

>>>>

%------------------------------------------------------------------------------
\subsection{Discovery and References}\label{sec:disc}

@@

%------------------------------------------------------------------------------
\subsection{Orbital Parameters}\label{sec:orbit}

We report the orbital parameters that determine the shape of the
planet's orbit. Depending on the detection methods, different sets of
parameters are given by the literatures. For instance, if a planet is
detected by the radial velocity method, the semiamplitude, $K$, is
reported whereas the inclination of the orbit, $i$, is reported by the
transit method. We describe the added fields since \cite{Wright2011}
below.

@@

%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

We report the transit parameters, which are available only when the
planet has TRANSIT flag equal to 1. We describe added fields since
\cite{Wright2011} below.

@@

%------------------------------------------------------------------------------
\subsection{Secondary Eclipse}\label{sec:se}

@@

%------------------------------------------------------------------------------
\subsection{Stellar Properties}\label{sec:stellarprop}

This set of parameters is to provide users the physical parameters of
the exoplanet host stars.  Most of the parameters are derived from the
stellar models in the literatures and we provide the readers with the
references. We describe added fields since \cite{Wright2011} below.

@@

%------------------------------------------------------------------------------
\subsection{Stellar Magnitudes}\label{sec:stellarmag}

@@

%------------------------------------------------------------------------------
\subsection{Coordinates and Catalogs}\label{sec:coord}
We report the coordinates of the host star as well as the stellar ID
as designated by different catalogs.  We added {\bf DIST} since
\cite{Wright2011}, which is the distance of the host star in the unit
of pc. If only parallax (PAR) is given, we convert it to DIST and vice
versa. If the literature does not report DIST or PAR, then we obtain
PAR from the Hipparcos data set by \cite{van Leeuwen2009}.

%------------------------------------------------------------------------------
\subsection{Uncertainties and Upper Limits}\label{sec:unc}

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
uncertainties, and they are different when the error bars are
asymmetric. UX contains the 1$\sigma$ uncertainty, and it equals to
$({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error bars. Fields
that have XUPPER, XLOWER and UX are: all the orbital parameters except
for TREND and FREEZE\_ECC flags; all the transit parameters except for
TRANSIT flags; all the secondary eclipse fields except for SE flag;
and all the stellar properties except for STAR, SPECREF and BINARY
flag; and DIST and PAR.

We also report the upper limits for planet mass (MSINI), eccentricity
(ECC), and the velocity semi-amplitude (K) when the literatures only
provide the upper limits and not the actual values. The upper limits
for ECC is reported when the orbit is circular, and the upper limits
for K is reported when there is no radial velocity detection. If only
upper limits are given, we set the field to 0, the uncertainty to half
of the upper limit, and the upper limits to the upper limits. For
example, if the literature reports the upper limit for ECC, then we
put the value in ECCUL, set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2.

%------------------------------------------------------------------------------
\subsection{References}\label{sec:ref}

@@

\begin{deluxetable}{llllc}
  \center

@@

  \colhead{Related Fields\tablenotemark{b}} & \colhead{Ref.}

@@

NAME\dotfill & String & Name of planet & \nodata & W11 \\
OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata & \ref{sec:disc} \\
DATE\dotfill & Integer & Year of publication of FIRSTREF & \nodata & W11 \\
MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata & W11 \\
PLANETDISCMETH\dotfill & String & Method of discovery of planet & \nodata & \ref{sec:disc} \\
STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata & \ref{sec:disc} \\
ORBREF\dotfill & String & Peer-reviewed origin of orbital parameters & ORBURL & W11 \\

@@

planetary orbit & FIRSTURL & W11 \\

@@

Planets Encyclopaedia & EPEURL & W11 \\

@@

Transit Database & ETDURL & W11 \\

@@

Archive database & EAURL & \ref{sec:disc} \\

@@

planet, if available) & SIMBADURL & W11 \\

@@

\nodata & \ref{sec:disc} \\
KOI\dotfill & Float & KOI object number & \nodata & \ref{sec:disc} \\
KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata & \ref{sec:disc} \\
EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata & \ref{sec:disc} \\
MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata & \ref{sec:disc} \\
IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata & \ref{sec:disc} \\
TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata & \ref{sec:disc} \\
ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata & \ref{sec:disc} \\

@@

function) in \mjup & -UL, -UPPER, etc. & W11 \\
MASS\dotfill & Float & Mass of planet in \mjup & -UPPER, etc. & \ref{sec:orbit} \\
A\dotfill & Float & Orbital semimajor axis in AU & -UPPER, etc. & W11 \\
SEP\dotfill & Float & Separation between host star and planet in AU & -UPPER, etc. & \ref{sec:orbit} \\
PER\dotfill & Double & Orbital period in days & -UPPER, etc. & W11 \\

@@

-UL, -UPPER, etc. & W11 \\
ECC\dotfill & Float & Orbital eccentricity & -UL, -UPPER, etc. & W11 \\
I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. & \ref{sec:orbit} \\
OM\dotfill & Float & Argument of periastron in degrees & -UPPER, etc. & W11 \\
BIGOM\dotfill & Float & Longitude of ascending node in degrees & -UPPER, etc. & \ref{sec:orbit} \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. & W11 \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER, etc. & W11 \\

@@

& -UPPER, etc. & \ref{sec:orbit} \\
TRANSIT\dotfill & Boolean & Is the planet known to transit? & -REF,-URL & W11 \\

@@

etc. & W11 \\

@@

HJD\tablenotemark{d} & -UPPER, etc. & W11 \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER, etc. & W11 \\
B\dotfill & Float & Impact parameter of transit & -UPPER, etc. & W11 \\
AR\dotfill & Float & $(a/R_*)$ & -UPPER, etc. & W11 \\
DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. & W11 \\

@@

-UPPER, etc. & W11 \\

@@

-UPPER, etc. & W11 \\
DR\dotfill & Float & Distance during transit in stellar radii & -UPPER, etc. & \ref{sec:transit} \\
RR\dotfill & Float & $(R_p/R_*)$ & -UPPER, etc. & \ref{sec:transit} \\

@@

CHI2\dotfill & Float & $\chi_{\nu}^2$ to orbital RV fit & \nodata & W11 \\
NOBS\dotfill & Integer & Number of observations used in fit & \nodata & W11 \\

@@

\nodata & W11 \\
FREEZE\_ECC\dotfill & Boolean & Eccentricity frozen in fit? & \nodata & W11 \\
TREND\dotfill  & Boolean & Linear trend in fit? & \nodata & W11 \\
NCOMP\dotfill & Integer & Number of planetary companions known & \nodata & W11 \\
MULT\dotfill & Boolean & Multiple planets in system? & \nodata & W11 \\
COMP\dotfill & String & Component name of planet ($b$, $c$, etc.) & \nodata & W11 \\

@@

been detected & -REF,-URL & \ref{sec:se} \\
SEDEPTHJ\dotfill & Float & Secondary eclipse depth in $J$ band & -UPPER, etc. & \ref{sec:se} \\
SEDEPTHH\dotfill & Float & Secondary eclipse depth in $H$ band & -UPPER, etc. & \ref{sec:se} \\

@@

band & -UPPER, etc. & \ref{sec:se} \\

@@

\kepler\ photometry band & -UPPER, etc. & \ref{sec:se} \\

@@

\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. & \ref{sec:se} \\

@@

\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. & \ref{sec:se} \\

@@

\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. & \ref{sec:se} \\

@@

\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. & \ref{sec:se} \\

@@

HJD\tablenotemark{d} & -UPPER, etc. & \ref{sec:se} \\

@@

STAR\dotfill & String & Standard name for host star & \nodata & W11 \\
BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL & W11 \\
MSTAR\dotfill & Float & Mass of host star in solar mass & -UPPER, etc. & W11 \\
RSTAR\dotfill & Float & Radius of host star in solar radii & -UPPER, etc. & \ref{sec:stellarprop} \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER, etc. & W11 \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER, etc. & W11 \\
RHOSTAR\dotfill & Float & Density of host star & -UPPER, etc. & \ref{sec:stellarprop} \\

@@

host star in cgs unit & -UPPER, etc. & W11 \\

@@

star in k\mps & -UPPER, etc. & W11 \\
GAMMA\dotfill & Float & Systemic radial velocity in k\mps & -UPPER, etc. & \ref{sec:stellarprop} \\

@@

V\dotfill & Float & $V$ magnitude & -REF,-URL & W11 \\
BMV\dotfill & Float & $B-V$ color & \nodata & W11 \\
J\dotfill & Float & $J$ magnitude & \nodata & W11 \\
H\dotfill & Float & $H$ magnitude & \nodata & W11 \\
KS\dotfill & Float & $K_S$ magnitude & \nodata & W11 \\
SHK\dotfill & Float & Mount Wilson Ca \sc{II} $S$-value & \nodata & \ref{sec:stellarmag} \\
RHK\dotfill & Float & Chromospheric activity of star as $R'_{HK}$ & \nodata & W11 \\
KP\dotfill & Float & \kepler\ bandpass magnitude & \nodata & \ref{sec:stellarmag} \\
SPECREF\dotfill & String & Source of most of the spectroscopic parameters & SPECURL & W11 \\

@@

RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata & W11 \\
RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  & W11 \\
DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata & W11 \\
DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata & W11 \\
PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- & W11 \\
DIST\dotfill & Float & Distance to host star based on parallax in parsecs & -UPPER, etc. & \ref{sec:coord} \\

@@

star & \nodata & W11 \\
HD\dotfill & Long Integer & Henry Draper number of sar & \nodata & W11 \\
GL\dotfill & Float & GJ or Gliese catalog number of star & \nodata & W11 \\
HR\dotfill & Integer & Bright Star Catalog number of star & \nodata & W11 \\
SAO\dotfill & Long Integer & SAO catalog number of star & \nodata & W11 \\

@@

column. They are... See Section~\ref{sec:unc} and \ref{sec:ref} for
more details. -UL stands for upper limits for the fields (see
Section~\ref{sec:unc} for details).}
